\begin{thebibliography}{99}
\footnotesize

%1
\bibitem{DUNE_CDR}
R. Acciarri {\it et al.}, ``Long-Baseline Neutrino Facility (LBNF) and Deep Underground Neutrino Experiment (DUNE) Conceptual Design Report Volume 1: The LBNF and DUNE Projects'', arXiv:1601.05471  [physics.ins-det].

%2
\bibitem{cenf}
CENF Project, \url{https://edms.cern.ch/nav/P:CERN-0000096725:V0/P:CERN-0000096728:V0/TAB3};M. Nessi, ``CERN Neutrino Platform'', ICFA Neutrino European Meeting, Paris, 8-10 January 2014. 

%3
\bibitem{lbnf@cern}
M. A. Leigui de Oliveria {\it et al.}, ``Expression of Interest for a Full-Scale Detector Engineering Test and Test Beam Calibration of a Single-Phase LAr TPC'',
CERN-SPSC-2014-027, SPSC-EOI-011.

%4
\bibitem{dual}
S. Murphy (on behalf of the WA105 collaboration),``The WA105-3x1x1 m3 dual phase LAr-TPC demonstrator'', (2016) arXiv:1611.05846v1 [physics.ins-det].

%5
\bibitem{nu_review}
C. Patrignani {\it et al.} (Particle Data Group), ``Neutrino Mass, Mixing, and Oscillation'', Chin. Phys. C, 40, 100001 (2016)

%6
\bibitem{LBNE}
C. Adams {\it et al.}, ``Scientific Opportunities with the Long-Baseline Neutrino Experiment'', arXiv:1307.7335 [hep-ex]; \url{http://lbne.fnal.gov}.

%7
\bibitem{1d}
C. Rubbia, ``The liquid argon time projection chamber: a new concept for neutrino detectors'', CERN-EP-INT-77-08 (1977).

%8
\bibitem{1e}
F. Arneodo {\it et al.}, ``The ICARUS Experiment, A Second-Generation Proton Decay Experiment and Neutrino Observatory at the Gran Sasso Laboratory'',arXiv:0103008 [hep-ex] (2001).

%9
\bibitem{1z}
P.~Aprili {\it et al.},
``The ICARUS experiment: A second-generation proton decay experiment and
neutrino observatory at the Gran Sasso laboratory. Cloning of T600 modules to
reach the design sensitive mass. (Addendum)'', 
LNGS-EXP 13/89 add.2/01, and CERN-SPSC-2002-027.

%10
\bibitem{nomad}
J. Altegoer {\it et al.}, ``The NOMAD experiment at the CERN SPS'', Nucl. Instrum. Meth. A 404 (1998) 96.

%11
\bibitem{microboone}
\url{http://www-microboone.fnal.gov}

%12
\bibitem{lar1nd}
C. Adams  {\it et al.}, ``LAr1-ND: Testing Neutrino Anomalies with Multiple LAr TPC Detectors at Fermilab'', arXiV:1309.7987 [physics.ins-det].

%13
\bibitem{1i}
M. Zeller {\it et al.}, ``Ionization signals from electrons and alpha-particles in mixtures of liquid Argon and Nitrogen - perspectives on protons for Gamma Resonant Nuclear 
Absorption applications'', JINST 5 (2010) 10009.

%14
\bibitem{1j}
B. Rossi {\it et al.}, ``A prototype liquid Argon Time Projection Chamber for the study of UV laser multi-photonic ionization'', JINST 4 (2009) 07011.

%15
\bibitem{1k}
A. Ereditato {\it et al.}, ``Study of ionization signals in a TPC filled with a mixture of liquid Argon and Nitrogen'', JINST 3 (2008) 10002.

%16
\bibitem{1l}
I. Badhrees {\it et al.}, ``Measurement of the two-photon absorption cross-section of liquid argon with a time projection chamber'', New J. Phys. 12 (2010) 113024.

%17
\bibitem{argontube1}
A. Ereditato {\it et al.}, ``Design and operation of ARGONTUBE: a 5 m long drift liquid argon TPC'', JINST 8 (2013) P07002.

%18
\bibitem{argontube2}
M. Zeller {\it et al.}, ``First measurements with ARGONTUBE, a 5m long drift Liquid Argon TPC'', Nucl. Instrum. Meth. A718 (2013) 454.

%19
\bibitem{argontube3}
I. Badhrees {\it et al.}, ``ARGONTUBE: An R\&D liquid Argon Time Projection Chamber'', JINST 7 (2012) C02011. 

%20
\bibitem{1m}
S. Amerio {\it et al.}, ``Design, construction and tests of the ICARUS T600 detector'', Nucl. Instrum. Meth. A 527 (2004) 329.

%21
\bibitem{Doke:nc}
T.~Doke,
``A Historical View On The R\&D For Liquid Rare Gas Detectors'',
Nucl.\ Instrum.\ Meth.\ A { 327} (1993) 113.

%22
\bibitem{Willis:1974gi}
W.~J.~Willis and V.~Radeka,
``Liquid Argon Ionization Chambers as Total Absorption Detectors'',
Nucl.\ Instrum.\ Meth.\  { 120} (1974) 221.

%23
\bibitem{Aprile:1985xz}
E.~Aprile, K.~L.~Giboni and C.~Rubbia,
``A Study of Ionization Electrons Drifting Large Distances in Liquid and Solid
Argon",
Nucl.\ Instrum.\ Meth.\ A { 241} 62 (1985).

%24
\bibitem{3tons}
P.~Benetti {\it et al.},
``A 3 Ton Liquid Argon Time Projection Chamber'', 
Nucl.\ Instrum.\ Meth.\ A { 332} (1993) 395;\\

%25
\bibitem{Cennini:ha}
P.~Cennini {\it et al.},
``Performance of a 3 Ton Liquid Argon Time Projection Chamber'',  
Nucl.\ Instrum.\ Meth.\ A { 345} (1994) 230.

%26
\bibitem{50lt}
F.~Arneodo {\it et al.},
``The ICARUS 50 l LAr TPC in the CERN neutrino beam'', 
arXiv:hep-ex/9812006.

%27
\bibitem{t600paper}
S.~Amerio {\it et al.},
``Design, construction and tests of the ICARUS T600 detector'',
Nucl. Instrum. Meth., A527 (2004) 329  and references therein.

%28
\bibitem{USeffort}
B.~Baller {\it et al.},
``Liquid Argon Time Projection Chamber Research and Development in the United States'', JINST 9 (2014) T05005;  arXiv:1307.8166v3.

%29
\bibitem{argoneut}
C.~Anderson {\it et al.},
``The ArgoNeuT Detector in the NuMI Low-Energy Beam Line at Fermilab'', JINST 7 (2012) P10019;
arXiV:1205.6747.

%30
\bibitem{icarusUSA}
M. Antonello {\it et al.}, ``ICARUS at FNAL'', arXiv:1312.7252 [physics.ins-det].
\url{http://www.fnal.gov/directorate/program\_planning/Jan2014PACPublic/ICARUS.pdf}

%31
\bibitem{ARAPUCA}
A.A. Machado and E. Segreto, ``ARAPUCA a new device for liquid argon scintillation light detection'', JINST 11 (2016) C02004.

%32
\bibitem{Martin_thesis}
M. Auger, ``New Micromegas based Readout techniques for Imaging in Time Projection Chambers'', PhD Thesis, Albert Einstein Center for Fundamental Physics, Universitat Bern.

%33
\bibitem{bnl-electronics}
V. Radeka {\it et al.}, iopscience.iop.org/1742-6596/308/1/012021/pdf/1742-6596\_308\_1\_012021.pdf

%34
\bibitem{topmetal}
M. An {\it et al.}, ``A Low-Noise CMOS Pixel Direct Charge Sensor, Topmetal-II'', arXiv:1509.08611v2 [physics.ins-det].

%35
\bibitem{bernHV}
A. Blatter {\it et al.}, ``Experimental study of electric breakdowns in liquid argon at centimeter scale'', JINST 9 (2014) P04006.%arXiv:1401.6693. 

%36
\bibitem{loi_old}
M. Auger {\it et al.}, ``ArgonCube: a novel, fully-modular approach for the realization of large-mass liquid argon TPC neutrino detectors'', (2015) CERN SPSC LoI 243.

%37
\bibitem{HVBD}
M. Auger {\it et al.}, ``On the Electric Breakdown in Liquid Argon at Centimeter Scale'', arXiv:512.05968v2 [physics.ins-det].

%38
\bibitem{CRT}
M. Auger {\it et al.}, ``Multi-channel front-end board for SiPM readout'', arXiv:1606.02290v1 [physics.ins-det].

%39
\bibitem{CRT2}
M. Auger {\it et al.}, ``A Novel Cosmic Ray Tagger System for Liquid Argon TPC Neutrino Detectors'', arXiv:1612.04614v1 [physics.ins-det].

%40
\bibitem{modtest}
D. Smargianaki and U. Kose ``Report for the test performed at BERN; The Module Box - Prototype '', CERN Project Document No:1728992 (2016)

%41
\bibitem{ehn1extension} EHN1 Hall Extension for Neutrino Detector R\&D Experiments, EDMS Document No. 1350076 v. 3.

%42
\bibitem{bernHV2}
M. Auger {\it et al.}, ``A method to suppress dielectric breakdowns in liquid argon ionization detectors for cathode to ground distances of several millimeters '', JINST 9 (2014) P07023.%arXiv:1406.3660. 
%43
\bibitem{wa105}
\url{http://laguna.ethz.ch:8080/Plone/wa105}

%44
\bibitem{wa105-2}
I. De Bonis {et al.}, ``Technical Design Report for Large-Scale Neutrino Detectors Prototyping and Phased Performance Assessment in View of a Longbaseline Oscillation Experiment'', CERN-SPSC-2014-013; SPSC-TDR-004.


\end{thebibliography}
\textbf{}